The Driving Forces of API Evolution

### 2015-06-04 thesis/paper.tex
Reverted author blocks
Removed Acknowledgements
Also added capitals to reference in the bib

\author{
% 1st. author
\alignauthor
John Burchell\\
       \affaddr{Computer Science and Engineering}\\
       \affaddr{University of Gothenburg}\\
       \email{john.a.burchell@gmail.com}
% 2nd. author
\alignauthor
William Granli\\
       \affaddr{Computer Science and Engineering}\\
       \affaddr{University of Gothenburg}\\
       \email{william.granli@gmail.com}
}

@@

\section*{Acknowledgements}
We would like to thank company A for allowing us to conduct this study in cooperation with them. We would also like to thank associate professor Imed Hammouda for assisting us with this research.

>>>>

\author{
% 1st. author
\alignauthor
John Burchell and William Granli\\
       \affaddr{Computer Science and Engineering}\\
       \affaddr{University of Gothenburg}\\
       \email{john.a.burchell@gmail.com},  \email{william.granli@gmail.com}
% 2nd. author
%\alignauthor
%William Granli\\
%       \affaddr{Computer Science and Engineering}\\
%       \affaddr{University of Gothenburg}\\
%       \email{william.granli@gmail.com}
%\and
% 3rd. author
\alignauthor Imed Hammouda and Eric Knauss\\
\affaddr{Computer Science and Engineering}\\
\affaddr{Chalmers $\mid$ University of Gothenburg}\\
\email{\{imed.hammouda,eric.knauss\}@cse.gu.se}
% 4th 
%\alignauthor Eric Knauss\titlenote{Co-author}\\
%       \affaddr{Computer Science and Engineering}\\
%       \affaddr{University of Gothenburg}\\
%       \email{imed.hammouda@gu.se}
}

@@
